\textbf{Response Letter}

### 2018-12-01 doc/aij18/major-revision/letter.tex
updates in response letter

We identified four main points to be addressed as per the reviewers' comments and observations. In this section, we provide details of these four main modifications, and we will point at them when replying to each of the reviewers' comments in the remainder sections.

>>>>

We identified three main points to be addressed as per the reviewers' comments and observations. In this section, we provide details of these three main modifications, and we will point at them when replying to each of the reviewers' comments in the remainder sections.
